---
title: "Homework_1_jg5037"
author: "Jian Gao"
date: "`r Sys.Date()`"
output: github_document
---
# Problem 1

## loading necessary package and dataset
```{r loading package}
#loading necessary package and dataset
library(moderndive)
library(ggplot2)
library(tidyverse)
data("early_january_weather")
```

## Summary the dataset

**The variables included in the dataset are: `r names(early_january_weather)`.** 

Key variables include:

  - **Temperature (`temp`)**: numeric, with an average of about `r     mean(early_january_weather$temp, na.rm = TRUE)` °F  
  - **Humidity (`humid`)**: numeric, ranging from `r min(early_january_weather$humid, na.rm = TRUE)` to `r max(early_january_weather$humid, na.rm = TRUE)`  
  - **Time (`time_hour`)**: This dataset record the observation time, ranging from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`  
  - Other variables include wind speed (`wind_speed`), precipitation (`precip`), and visibility (`visib`).  

## Creat the scatterplot of (`temp`) VS (`time_hour`)

```{r creat plot,fig.width=7, fig.height=5}
# Define the plot
scatterplot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point(alpha = 0.7) +
  labs(
    title = "Temperature vs Time (colored by humid)",
    x = "Time (hour)",
    y = "Temperature (F)",
    color = "humid"
  )

# Show the ggplot
scatterplot

# Save to project directory
ggsave("scatter_temp_time.png", scatterplot, width = 7, height = 5)
```
# Problem 2

## Creat the  required data_frame
```{r creat data_frame}
set.seed(1) # For repeat(not change the data frame)

df <- tibble(
  num_var = rnorm(10), # Random select 10 numbers from normal distribution
  log_var = rnorm(10) > 0, # Show that if the sample are greater than 0
  char_var = letters[1:10], # Character vector of length 10
  fac_var = factor(rep(c("A", "B", "C"), length.out = 10)) # Factor vector of length 10, with three different factor levels.
)
# Show the data_frame
df
```

## Testing each veriable to take mean value
```{r test different types of variables}
mean_num <- mean(df %>% pull(num_var))
mean_num
mean_log <- mean(df %>% pull(log_var))
mean_log
mean_char <- mean(df %>% pull(char_var))
mean_char
mean_fac <- mean(df %>% pull(fac_var))
mean_fac
```

### Results and Interpretation

_When calculating the mean of each variable:_

- **Numeric (`num_var`)**: mean is `r mean(df %>% pull(num_var))` → works as expected since it is numeric data.  
- **Logical (`log_var`)**: mean is `r mean(df %>% pull(log_var))` → works because `TRUE` is return to 1 and `FALSE` return 0; the mean given by  `TRUE` values.  
- **Character (`char_var`)**: Returns `NA` with a warning → characters are not numeric variables can not be calculated mean.  
- **Factor (`fac_var`)**: Returns `NA` with a warning : factors are categorical variables and cannot be directly averaged.  

**Summary:**  
Only numeric and logical variables can be meaningfully averaged. Character and factor variables can not direct computation of the mean.

## Change the non-working types variables by `as.numeric()`

```{r Change the different types variables}
new_log_var <- df %>%
  pull(log_var) %>%
  as.numeric()
new_log_var
new_char_var <- df %>%
  pull(char_var) %>%
  as.numeric()
new_char_var
new_fac_var <- df %>%
  pull(fac_var) %>%
  as.numeric()
new_fac_var
```
### Results and Interpretation

- **Logical to Numeric**  
  `TRUE` is return to 1 and `FALSE` return to 0.  
  The mean gives the proportion of `TRUE` values so that the logical variables can be averaged.

- **Character to Numeric**  
  Characters such as `"a"`, `"b"`, `"c"` cannot be directly converted.  
  The result is `NA` with a warning (`NAs introduced by coercion`), so their mean cannot be computed.  

- **Factor to Numeric**  
  Factors are internally stored as integer codes corresponding to their levels (e.g., level A = 1, level B = 2, level C = 3).  
  Conversion returns these values(levels), so technically a mean can be calculated
**Summary:**  
- Numeric and logical variables can be meaningfully averaged.  
- Character variables convert to `NA` and cannot be averaged.  
- Factor variables convert to integer codes, but their mean has no real-world meaning.
