---
title: "Homework_1_jg5037"
author: "Jian Gao"
date: "`r Sys.Date()`"
output: github_document
---
# Problem 1

## Part a
```{r}
library(moderndive)
library(ggplot2)
data("early_january_weather")
```

The variables included in the dataset are: `r names(early_january_weather)`.  

Key variables include:  
- **Temperature (`temp`)**: numeric, with an average of about `r round(mean(early_january_weather$temp, na.rm = TRUE), 1)` °F  
- **Humidity (`humid`)**: numeric, ranging from `r round(min(early_january_weather$humid, na.rm = TRUE),1)` to `r round(max(early_january_weather$humid, na.rm = TRUE),1)`  
- **Time (`time_hour`)**: POSIXct variable recording the observation time, ranging from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`  
- Other variables include wind speed (`wind_speed`), precipitation (`precip`), and visibility (`visib`).  

```{r fig.width=7, fig.height=5}
library(ggplot2)

p <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point(alpha = 0.7) +
  labs(
    title = "Temperature vs Time (colored by humidity)",
    x = "Time (hour)",
    y = "Temperature (F)",
    color = "Humidity"
  ) +
  theme_minimal()

# show the ggplot
p

# Save to project directory
ggsave("scatter_temp_time.png", p, width = 7, height = 5)
```

